\Huge Conferences in the Era of Expensive Carbon

### 2019-07-16 main.tex
Working on Richard comments

@@

@@

The climate crisis is too important to ignore and too urgent to leave for
world leaders to address at their own pace: Organizations at every scale
must confront their own contributions, raise awareness among their members,
and establish new ways of doing business in the lower-carbon future that is
coming at us.  We in ACM must play our part.

>>>>

\bcp{Richard Kim sent a bunch of great comments!  In particular...
  \begin{itemize}
  \item (a) You might say something more about how ACM is in a good position
  to set a trend -- something about taking leadership among scientific
  societies or being on the forefront. There's a little bit about this at
  the end, but it might be developed more into a sentence or paragraph. You
  probably want to phrase this as leadership as opposed to say, sticking
  one's neck out, but there could be something about how computer science &
  tech folks are current and forward-looking, and it's consistent that we
  not be behind the leading edge.
  \item (b) You might say more how ACM needs to prepare itself in light of
  the trends that are coming -- carbon pricing is good organizational sense!
  There's some of this around ACM's potentially needing to adjust its
  business model, but it falls short of making a *business case for carbon
  pricing*, which is what I guess I'm recommending.
  \item Also, in addition to mentioning that Microsoft and other tech
  companies set a price on carbon, you might also note here that Exxon and
  other energy companies set an internal price on carbon as well, as a means
  of risk assessment. In other words, even the oil companies know what's
  coming.
  \end{itemize}
}

@@

\bcp{See comments at this point about companies (MS, Google?) that are
  already doing this.}
% You probably know about Microsoft using an internal price for carbon  - it's mentioned here:
% https://unfccc.int/climate-action/momentum-for-change/financing-for-climate-friendly/microsoft-global-carbon-fee
% And this report is also instructive:
% https://download.microsoft.com/download/0/A/B/0AB2FDD7-BDD9-4E23-AF6B-9417A8691CF5/Microsoft%20Carbon%20Fee%20Impact.pdf

@@

The climate crisis is too urgent to leave for
world leaders to address at their own pace: Organizations at every scale
must confront their own contributions, raise awareness among their members,
and establish new ways of doing business in the lower-carbon future that is
coming at us.  We in ACM must play our part.
